---
title: "Exploring the Cars Dataset"
author: "Joe Collins"
format:
  html:
    toc: true
    code-fold: true
    theme: cosmo
    css: styles.css
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
execute:
  echo: true
---

# Introduction

The `cars` dataset is included with R. It contains the speed of cars and the distances taken to stop.

## Load the data

```{r}
data(cars)

head(cars)
summary(cars)
```

## Scatter Plot

```{r}
plot(
  cars$speed,
  cars$dist,
  pch = 19,
  xlab = "Speed (mph)",
  ylab = "Stopping Distance (ft)",
  main = "Cars Dataset"
)
```

## Linear Regression

```{r}
model <- lm(dist ~ speed, data = cars)

summary(model)
```

## Regression Plot

```{r}
plot(
  cars$speed,
  cars$dist,
  pch = 19,
  xlab = "Speed (mph)",
  ylab = "Stopping Distance (ft)"
)

abline(model, col = "red", lwd = 2)
```

## Conclusions

The analysis suggests:

- Stopping distance increases with speed.
- A simple linear regression explains a substantial proportion of the variation.
- The relationship is approximately linear.